### 2014-02-27 paper/formal.tex
rm formal from retrofit.tex

\subsection{Security guarantees}
\label{sec:retrofit:formal}

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
%
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwsie, apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.\footnote{
We note that the definition of |erasef il| precisely captures the IFC
language's attacker model.  For instance, in our case, by removing sensitive
tasks and messages from the system, we assume that that the attacker cannot
observe the number of sensitive tasks or messages.
}
%
%}

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase l tS) (erase l ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|
\end{align*}
\caption{
Erasure function for tasks, queue maps, message queues, and configurations.
In all other cases, including target-language constructs, |erasef il| is
applied homomorphically.
\label{fig:erasure}
}
\end{figure}

>>>>

\section{Security guarantees}
\label{sec:formal}

@@

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
%
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwsie, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.

We note that the definition of |erasef il| precisely captures the IFC
language's attacker model.  For instance, in our case, by removing sensitive
tasks and messages from the system, we assume that that the attacker cannot
observe the number of sensitive tasks or messages.
%
%}

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' (erase l tS) (erase l ie)| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
\end{align*}
\caption{
Erasure function for tasks, queue maps, message queues, and configurations.
In all other cases, including target-language constructs, |erasef il| is
applied homomorphically.
\label{fig:erasure}
}
\end{figure}
